Dynein project log

### 2016-08-15 thesis_stuff/thesis_stuff.tex

>>>>

\section{Biochemistry Papers}

\subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}
-Communication between motors and BDs possible through $\alpha$-helix sliding. Bidirectional communication. [24,25]\\
-Pre, post-powerstroke states\\
-Pre-powerstroke: unbound state after ATP hydrolysis (our onebound)\\
-Post-powerstroke: bound state (our bothbound)\\
-Elastic stalk, unlike our rigid one\\
-Only tail angle changes between pre and post-powerstroke\\
-MTBD decides directionality?\\
-Tail-tail interaction, also motor-motor stacking interaction\\
-rate constant simulation, does not do dynamics to take into account time spent in a state\\

\subsection{Physical Parameters from Winch Model paper}
Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when
prestroke.
